---
title: "Business Intelligence Project"
author: "Adrianna Bitutu Ndubi"
date: "15th October 2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        | 134126 |
| **Student Name**                             | Ndubi Adrianna Bitutu |
| **BBIT 4.2 Group**                           | Fearless Achievers|
| **BI Project Group Name/ID (if applicable)** | ... |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset

### Source:

The dataset that was used can be downloaded here: *\<https://docs.google.com/spreadsheets/d/1LwVZIklzc0JvyVPQul9CxGnu2spipZjXaCO_Zv8H2sc/edit#gid=2007896421>*

### Reference:

*\<Cite the dataset here using APA\>\
Refer to the APA 7th edition manual for rules on how to cite datasets: <https://apastyle.apa.org/style-grammar-guidelines/references/examples/data-set-references>*

```{r Dataset Loader}
library(readr)

# Provide the executable R code inside the various code chunks as guided by the
# lab work.
```### The Normalize Transform on the student_performance_dataset Dataset ----
summary(student_performance_dataset)
model_of_the_transform <- preProcess(student_performance_dataset, method = c("range"))
print(model_of_the_transform)
student_performance_dataset_normalize_transform <- predict(model_of_the_transform, # nolint
                                                           student_performance_dataset)
summary(student_performance_dataset_normalize_transform)

### The Standardize Basic Transform on the student_performance_dataset Dataset ----
# BEFORE
summary(student_performance_dataset)
sapply(student_performance_dataset[, 1:8], sd)

model_of_the_transform <- preProcess(student_performance_dataset,
                                     method = c("scale", "center"))
print(model_of_the_transform)
student_performance_dataset_standardize_transform <- predict(model_of_the_transform, # nolint
                                                             student_performance_dataset)

# AFTER
summary(student_performance_dataset_standardize_transform)
sapply(student_performance_dataset_standardize_transform[, 1:8], sd)



